I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-01-16 Paper/proofs.tex
update proof

	First, notice that if $\Val_{\vx}(b)$ is maximal (resp. minimal), 
	then $\Val_{\boldsymbol{x}}(\hat{b})$ also gets maximal (resp. minimal).
	The following definition is the most important concept in this proof.

@@

@@

				\begin{definition}
					Let $K$ be the set of  all input nodes $a_k$. 
					We define a decomposition $K=I\sqcup J$ as follows:  
					\begin{itemize}
						\item $a_k \in I$  if
						\begin{enumerate}
							\item every path from $a_k$ to $z$ has weight $\geq 0$, or
							\item every path from $a_k$ to $z$ has weight $\leq 0$.
						\end{enumerate}
						That is, $a_k$ is not a source of a weak compensating pair.
						\item $a_k \in J$ if $a_k \notin I$, that is there exists two paths $\pi,\pi'$ from $k$, 
						one with positive and one with negative weight.
					\end{itemize}
				\end{definition}

>>>>

	First, notice that if $\Val_{\vx}(b)$ is maximal (resp. minimal), 
	then $\Val_{\boldsymbol{x}}(\hat{b})$ also gets maximal (resp. minimal).

	For convenience, when we discuss about the maximal or minimal values for nodes $n$ in a network, we write $\max(n),\min(n)$ directly, instead of $\max(\Val(n))$, $\min(\Val(n))$ or $\max_{\vx}(\Val_{\vx}(n)),\min_{\vx}(\Val_{\vx}(n))$.

	The following definition is the most important concept in this proof.

@@

	Using the concept of sign, now we introduce the key lemma for our theorem.

	\begin{lemma}\label{lem:key1}

		Let $\vx^{*}$ be the input vector that for every node $a_i$, if $S(a_i)=1$, then $x_{a_i}$ is the maximal value of $a_i$, and if $S(a_i)=-1$, then $x_{a_i}$ is the minimal value of $a_i$ ($S(a_i)=0$, then $x_{a_i}$ be an arbitrary fixed value in the input interval of $a_i$).

		Then the input $\vx^*$ maximize all nodes $n$ that $S(n)=1$ and minimize all nodes $n$ that $S(n)=1$.
	\end{lemma}

	\begin{proof}
		We prove this lemma by induction. For input layer, this is true by definition. Suppose this lemma is true up to layer $L_i$, we need to show this for layer $L_{i+1}$. Let $c$ be a node in layer $L_{i+1}$, then by definition, we have the following equation: \begin{align*}
			c = \boldsymbol{bias}_c+\sum_{b\in L}W_{bc}\ReLU(b).
		\end{align*}

		Therefore we have the following inequalities:\begin{align*}
				\max(\Val(c))\leq\sum_{b \in L_i, W_{bc n}>0}W_{bc} \max(\Val(\hat{b})) + \sum_{b \in L_i, W_{bc}<0}W_{bc} \min(\Val(\hat{b})) + \boldsymbol{bisa}_c\\
			\min(\Val(c))\geq\sum_{b \in L_i, W_{bc n}>0}W_{bc} \min(\Val(\hat{b})) + \sum_{b \in L_i, W_{bc}<0}W_{bc} \max(\Val(\hat{b})) + \boldsymbol{bisa}_c
		\end{align*}

		Now, if $S(c)=1$, we consider different case of $b$. If $S(b)=1$, then by Lemma \ref{lem:sign}, $W_{bc}>0$; if $S(b)=-1$, then $W{bc}<0$; if $S(b)=0$, then $W_{bc}=0$.

		Combining with

@@

				\begin{definition}
					We define a decomposition of the input nodes set to be $A_{pure}\sqcup A_{open}$ as follows:  
					\begin{itemize}
						\item $a_k \in A_{pure}$  if
						\begin{enumerate}
							\item every path from $a_k$ to $z$ has weight $\geq 0$, or
							\item every path from $a_k$ to $z$ has weight $\leq 0$.

						\end{enumerate}
						That is, $a_k$ is not a source of a weak compensating pair. 	We write $A_{pure}$ by $I$ for short.
						\item $a_k \in A_{open}$ if $a_k \notin A_{pure}$, that is there exists two paths $\pi,\pi'$ from $k$, 
						one with positive and one with negative weight. 	We write $A_{open}$ by $J$ for short.
					\end{itemize}
				\end{definition}
